SecureIt: home security has never been so easy\\ Anno Accademico 2011/2012

### 2012-12-25 relazioni/wireless/paper.tex
Eliminato file temporaneo che non so che abbia creato e sistemato logaritmo relazione palazzi

In order to exploit those tables and the user-friendliness of decibel \texttt{PCM} values are used to get \texttt{dB} values.\\ 
Referring to a measure of power or intensity we can express the ratio between current value $V_i$ and a reference value $V_o$ in decibels as:\\

\begin{equation}
dB_i = 10log_{10} \left(\frac{V_i}{V_o}\right)
\end{equation}

@@

Audio is captured by Android phone using \texttt{AAC} encoding, unfortunately firefox does not support \texttt{HTML5 ACC} encoding. In order to make audio available for all modern browser as soon as it is received by the web application it is converted into \texttt{MP3} encoding using \texttt{FFMPEG}:

\begin{lstlisting}[language=Bash, caption=FFMPEG command to convert aac to mp3]
ffmpeg -i in.m4a -vn -acodec libmp3lame ou.mp3
\end{lstlisting}

>>>>

In order to exploit those tables and the user-friendliness of decibel \texttt{PCM} values are used to get \texttt{dB} values.\\ 
Referring to a measure of amplitude we can express the ratio of the squares between current value $V_i$ and a reference value $V_o$ in decibels as:\\

\begin{equation}
dB_i = 20log_{10} \left(\frac{V_i}{V_o}\right)
\end{equation}

@@

Audio is captured by Android phone using \texttt{AAC} encoding, unfortunately Firefox and other browsers do not support \texttt{ACC} encoding. In order to make audio available for all modern browser as soon as it is received by the web application it is converted into \texttt{vorbis} encoding using \texttt{ffmpeg}:

\begin{lstlisting}[language=Bash, caption=FFMPEG command to convert aac to mp3]
ffmpeg -i in.m4a -acodec libvorbis -aq 60 -vn -ac 2 out.ogg
\end{lstlisting}
